MODELLING THE CO-EVOLUTION OF TRADE AND CULTURE IN PAST SOCIETIES

### 2015-07-20 article.tex
revision etape 3 miss Xavi Bio and Bigger Legend

\usepackage{algorithm,algorithmicx,algpseudocode}
\usepackage{float}
\usepackage{booktabs}
 \usepackage{multirow}
  \usepackage[a4paper,pagebackref,hyperindex=true]{hyperref}
\usepackage{color}
\definecolor{linkcol}{rgb}{0,0,0.4} 
\definecolor{citecol}{rgb}{0.5,0,0} 
\definecolor{pylabgreen}{RGB}{0,128,0}
\definecolor{pylabpink}{RGB}{255,192,203}
\definecolor{pylabblue}{RGB}{36,36,255}
\definecolor{pylabgrey}{RGB}{128,128,128}
\hypersetup
{
bookmarksopen=false,
pdftitle=Modelling the Co-evolution of Trade and Culture in Past Societies,
pdfauthor="Carrignon Montanier Rubio-Campillo", %auteur du document
pdfsubject="", %sujet du document
%pdftoolbar=false, %barre d'outils non visible
pdfmenubar=true, %barre de menu visible
pdfhighlight=/O, %effet d'un clic sur un lien hypertexte
colorlinks=true, %couleurs sur les liens hypertextes
pdfpagemode=None, %aucun mode de page
pdfpagelayout=SinglePage, %ouverture en simple page
pdffitwindow=true, %pages ouvertes entierement dans toute la fenetre
linkcolor=linkcol, %couleur des liens hypertextes internes
citecolor=citecol, %couleur des liens pour les citations
urlcolor=linkcol %couleur des liens pour les url
}

@@

\usepackage{xcolor}
    \usepackage{cite}

@@

@@

\title{Modelling the Co-evolution of Trade and Culture in Past Societies}

\maketitle

\begin{figure*}[htb]
{
\centering
Simon Carrignon\\ 
Jean-Marc Montanier\\
Xavier Rubio-Campillo\\
\vspace{12pt}
Barcelona Supercomputing Center\\
Carrer de Jordi Girona, 29, \\
08034 Barcelona, Spain\\
}
\end{figure*}

@@

The neutral model is tested through 15 experimental setups. The first six experimental setups are using 1 good, two population sizes (250 and 500 agents) and three values of $\mu$ (0.004,0.016 and 0.064). The remaining experimental setups are using 500 agents, 3 number of goods (3,6 and 9) and three values of $\mu$ (0.004,0.016 and 0.064). For each setup, we have performed 100 runs of 10000 timestep each. The trading model is tested on an experimental setups using 3 goods, 500 agents and $\mu$ equal to 0.004. Again 100 runs of 10000 timesteps are performed. The complete set of parameters tested on both models is presented in table~\ref{tab:parameters}. The experiments are available online\footnote{\href{https://github.com/montanier/CMR-WSC-CoEvolutionTradeCulture}{https://github.com/montanier/CMR-WSC-CoEvolutionTradeCulture}} for the Pandora simulator~\cite{rubiocampillo_2014}.

@@

\begin{table}
\begin{center}
\begin{tabular}{@{}ll@{}}
\toprule
Parameter & Value \\
\midrule
Number of goods & $\{1,3,6,9\}$ \\
Number of agents & $\{250,500\}$ \\
Innovation probability ($\mu$) & $\{0.004,0.016,0.064\}$ \\
Innovation range ($\beta$) & 0.005\\
Cultural transmission probability & .001\\
CulturalStep &  10 \\
TradeThreshold & 100  \\
TimeSteps & 10000 \\
\bottomrule
\end{tabular}
\caption{Table of parameters}\label{tab:parameters}
\end{center}
\end{table}

@@

\todo{complete table with final result (here it's just false exemple)}
\begin{table}[!h]
	\centering
	\begin{tabular}{cc|ccc}
		\multicolumn{2}{r}{}&\multicolumn{2}{c}{Our result}&\multicolumn{1}{c}{Bentley et. al. 2004}\\
			N&$\mu$ & $\alpha$ ($sd$) & $p$-value ($sd$ - $pr$) &$\alpha$ ($sd$)\\\hline
		250	&0.004&1.53 (0.03)&0.58 (0.24 - .01)&1.54 (0.02)\\
			&0.016&1.57 (0.02)&0.35 (0.28 - .05)&1.57 (0.01)\\
			&0.064&1.66 (0.01)&0.0 (0.00 - 1)&1.67 (0.01)\\\hline
		500	&0.004&1.50 (0.02)&0.59 (0.28 - .02 )&1.53 (0.03)\\
			&0.016&1.55 (0.03)&0.15 (0.17 - .10 )&1.61 (0.04)\\
			&0.064&1.78 (0.08)&0.0 (0.00 - 1)&1.81 (0.10)\\
	\end{tabular}
	\caption{Mean $\alpha$ \& $sd$ are calculated on 100 runs for our results, and 5 runs for Bentley et. al. 2004. $pr$ is the percentage of run for which the $p$-value is less than 0.05, i.e. the percentage of runs for which we rejected the null-hypotheses stating that the distribution follow a power law.}
	\label{tab:mualpha}
\end{table}

@@

\section{Acknowledgements}

@@

\bibliographystyle{wsc}
\bibliography{wsc.bib}  
\end{document}

>>>>

\usepackage{algorithm,algorithmicx,algpseudocode}
\usepackage{float}
\usepackage{booktabs}
 \usepackage{multirow}
  %\usepackage[a4paper,pagebackref,hyperindex=true]{hyperref}
\usepackage{color}
\definecolor{linkcol}{rgb}{0,0,0.4} 
\definecolor{citecol}{rgb}{0.5,0,0} 
\definecolor{pylabgreen}{RGB}{0,128,0}
\definecolor{pylabpink}{RGB}{255,192,203}
\definecolor{pylabblue}{RGB}{36,36,255}
\definecolor{pylabgrey}{RGB}{128,128,128}

%\hypersetup
%{
%bookmarksopen=false,
%pdftitle=Modelling the Co-evolution of Trade and Culture in Past Societies,
%pdfauthor="Carrignon Montanier Rubio-Campillo", %auteur du document
%pdfsubject="", %sujet du document
%%pdftoolbar=false, %barre d'outils non visible
%pdfmenubar=true, %barre de menu visible
%colorlinks=true, %couleurs sur les liens hypertextes
%pdfpagemode=None, %aucun mode de page
%pdfpagelayout=SinglePage, %ouverture en simple page
%pdffitwindow=true, %pages ouvertes entierement dans toute la fenetre
%linkcolor=black, %couleur des liens hypertextes internes
%citecolor=black, %couleur des liens pour les citations
%urlcolor=linkcol %couleur des liens pour les url
%}

@@

\usepackage{xcolor}

\usepackage{cite}

@@

\usepackage[pdftex,colorlinks=true,urlcolor=blue,citecolor=black,
anchorcolor=black,linkcolor=black,pdftitle=Modelling the Co-evolution of Trade and Culture in Past Societies,pdfauthor="Carrignon Montanier Rubio-Campillo"]{hyperref}

@@

\title{MODELLING THE CO-EVOLUTION OF TRADE AND CULTURE IN PAST SOCIETIES}

\author{Simon Carrignon\\ 
	Jean-Marc Montanier\\
	Xavier Rubio-Campillo\\[12pt]
	Barcelona Supercomputing Center\\
	Carrer de Jordi Girona, 29, \\
	Barcelona, 08034, SPAIN
}
\maketitle

@@

The neutral model is tested through 15 experimental setups. The first six experimental setups are using 1 good, two population sizes (250 and 500 agents) and three values of $\mu$ (0.004,0.016 and 0.064). The remaining experimental setups are using 500 agents, 3 number of goods (3,6 and 9) and three values of $\mu$ (0.004,0.016 and 0.064). For each setup, we have performed 100 runs of 10000 timestep each. The trading model is tested on an experimental setups using 3 goods, 500 agents and $\mu$ equal to 0.004. Again 100 runs of 10000 timesteps are performed. The complete set of parameters tested on both models is presented in table~\ref{tab:parameters}. The experiments are \href{https://github.com/montanier/CMR-WSC-CoEvolutionTradeCulture}{available online} \cite{github_2015} for the Pandora simulator~\cite{rubiocampillo_2014}.

@@

\begin{table}
\caption{Table of parameters}\label{tab:parameters}
	\scriptsize
\begin{center}
\begin{tabular}{@{}ll@{}}
\toprule
Parameter & Value \\
\midrule
Number of goods & $\{1,3,6,9\}$ \\
Number of agents & $\{250,500\}$ \\
Innovation probability ($\mu$) & $\{0.004,0.016,0.064\}$ \\
Innovation range ($\beta$) & 0.005\\
Cultural transmission probability & .001\\
CulturalStep &  10 \\
TradeThreshold & 100  \\
TimeSteps & 10000 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}

@@

\todo{complete table with final result (here it's just false exemple)}
\begin{table}[!h]
	\caption{Mean $\alpha$ \& $sd$ are calculated on 100 runs for our results, and 5 runs for Bentley et. al. 2004. $pr$ is the percentage of run for which the $p$-value is less than 0.05, i.e. the percentage of runs for which we rejected the null-hypotheses stating that the distribution follow a power law.}
	\centering
	\scriptsize
	\begin{tabular}{cc|ccc}
		\multicolumn{2}{r}{}&\multicolumn{2}{c}{Our result}&\multicolumn{1}{c}{Bentley et. al. 2004}\\
			N&$\mu$ & $\alpha$ ($sd$) & $p$-value ($sd$ - $pr$) &$\alpha$ ($sd$)\\\hline
		250	&0.004&1.53 (0.03)&0.58 (0.24 - .01)&1.54 (0.02)\\
			&0.016&1.57 (0.02)&0.35 (0.28 - .05)&1.57 (0.01)\\
			&0.064&1.66 (0.01)&0.0 (0.00 - 1)&1.67 (0.01)\\\hline
		500	&0.004&1.50 (0.02)&0.59 (0.28 - .02 )&1.53 (0.03)\\
			&0.016&1.55 (0.03)&0.15 (0.17 - .10 )&1.61 (0.04)\\
			&0.064&1.78 (0.08)&0.0 (0.00 - 1)&1.81 (0.10)\\
	\end{tabular}
	\label{tab:mualpha}
\end{table}

@@

\section*{ACKNOWLEDGEMENTS}

@@

\bibliographystyle{wsc}
\bibliography{wsc.bib}

\section*{AUTHOR BIOGRAPHIES}
\noindent {\bf SIMON CARRIGNON} is a PhD student at the Pompeu Fabra University. He holds a M.S. in in Cognitive Sciences and a M.A. in History and Philosophy of Science. His work focus on the use of computer modeling and evolutionary method to study Complex Systems. His email address is \email{simon.carrignon@bsc.es}.

\noindent {\bf JEAN-MARC MONTANIER} has obtained his engineering title in the domain of embedded computing. Since then, he has complete a Ph.D. in collective robotics at Universit\'e Paris-Sud XI. The topic of this Ph.D. was focused on the adaptation of a swarm of robots to unknown environments. His latest work in this area has addressed the learning of cooperative strategies, as well as the division of labour. He is now working in a new domain which proposes to apply Agent-Based Models to study economical and cultural evolution. His email address is \email{jeanmarc.montanier@bsc.es}.

\noindent {\bf XAVIER RUBIO-CAMPILLO}

\end{document}
